Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/intro.tex
Future work removed
intro and relwk nits

To evaluate whether Nail's design is effective at handling real-world data
formats, we implemented a prototype of Nail for C\@. Using our prototype, we
implemented succinct grammars for parts of an IP network stack, for DNS packets,
and for ZIP files, each in about a hundred lines of grammar. On top of these
grammars, we were able to build a DNS server in under 200 lines of C code, and
an {\tt unzip} utility in about 50 lines of C code, with performance comparable
to or exceeding existing implementations.This suggests both that Nail is
effective at handling complex real-world data formats, and that Nail makes it
easy for application developers to parse and generate external data
representations. Performance results show that the Nail-based DNS server
outperforms the widely used BIND DNS server, demonstrating that Nail-based
parsers and generators can achieve good performance.

The rest of this paper is organized as follows.  \S\ref{s:relwk}
puts Nail in the context of related work.
\S\ref{s:motivation} motivates the need for Nail by examining
past data format vulnerabilities.
\S\ref{s:design} describes
Nail's design.  \S\ref{s:impl} discusses our initial implementation
of Nail.  \S\ref{s:eval} provides evaluation results.
\S\ref{s:future} suggests several directions for future work, and
\S\ref{s:concl} concludes.

>>>>

To evaluate whether Nail's design is effective at handling real-world data
formats, we implemented a prototype of Nail for C\@. Using our prototype, we
implemented succinct grammars for parts of an IP network stack, for DNS packets,
and for ZIP files, each in about a hundred lines of grammar. On top of these
grammars, we were able to build a DNS server in under 200 lines of C code, and
an {\tt unzip} utility in about 50 lines of C code, with performance comparable
to or exceeding existing implementations. This suggests both that Nail is
effective at handling complex real-world data formats, and that Nail makes it
easy for application developers to parse and generate external data
representations. Performance results show that the Nail-based DNS server
outperforms the widely used BIND DNS server, demonstrating that Nail-based
parsers and generators can achieve good performance.

The rest of this paper is organized as follows.  \S\ref{s:relwk}
puts Nail in the context of related work.
\S\ref{s:motivation} motivates the need for Nail by examining
past data format vulnerabilities.
\S\ref{s:design} describes
Nail's design.  \S\ref{s:impl} discusses our implementation
of Nail.  \S\ref{s:eval} provides evaluation results, and
\S\ref{s:concl} concludes.

### 2014-05-02 paper/osdi14/relwk.tex
intro and relwk nits

Parser generators for binary protocols were first introduced by the
Hammer~\cite{hammer-parser} parser.
While previous parser generators could also be used to write grammars
for binary protocols,\footnote{Theoretically speaking, the alphabet
over which a grammar is an abstract set, so most algorithms work
just as well on an alphabet of $\{0,1\}$.} doing so is practically
inconvenient. Hammer allows the programmer to specify a grammar in
terms of bits and bytes instead of characters. Common concerns, such as
endianness and bit-packing are handled transparently.

@@

Generated parsers have long been used to parse human input, such
as programming languages and configuration files. Frequently, such
languages are often specified with a formal grammar in an executable
form. Unfortunately, parser frameworks are seldom used to recognize
machine-created input; as we demonstrate in \S\ref{s:eval},
state-of-the-art parser generators are not suitable for parsing or
generating many real-world data formats.

>>>>

Parser generators for binary protocols were first introduced by the
Hammer~\cite{hammer-parser} parser.
While previous parser generators could also be used to write grammars
for binary protocols,\footnote{Theoretically speaking, the alphabet
over which a grammar is an abstract set, so most algorithms work
just as well on an alphabet of $\{0,1\}$.} doing so is practically
inconvenient. Hammer allows the programmer to specify a grammar in
terms of bits and bytes instead of characters. Common concerns, such as
endianness and bit-packing, are handled transparently.

@@

Generated parsers have long been used to parse human input, such
as programming languages and configuration files. Frequently, such
languages are specified with a formal grammar in an executable
form. Unfortunately, parser frameworks are seldom used to recognize
machine-created input; as we demonstrate in \S\ref{s:eval},
state-of-the-art parser generators are not suitable for parsing or
generating many real-world data formats.
